Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-11-23 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Minor typo
Fig 1 revised

## The Shannon Entropy
The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
\end{equation}
here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.

@@

```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
L <- c(1, 3, 8, 12, 100)

L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line() +
  theme_minimal() +
  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
  labs(col = "Looks") +
  xlab(expression(paste(mu))) +
  theme(text=element_text(family="serif"))

>>>>

## The Shannon Entropy
The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
\end{equation}
here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.

@@

```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="The Shannon Entropy under the Gamma SAR model."}
L <- c(1, 3, 8, 12, 100)

L_labels <- c(expression(italic(L)==1), 
              expression(italic(L)==3), 
              expression(italic(L)==8), 
              expression(italic(L)==12), 
              expression(italic(L)==100))

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line(linewidth=2) +
  theme_minimal() +
  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
  labs(col = "Looks") +
  xlab(expression(paste(mu))) +
  theme(text=element_text(family="serif", size = 14),
        legend.position = "top")
